---
title: "p8105_hw1_jy3186"
output: github_document
date: "2022-09-18"
author: "Jiayi Yang"
---

## R Markdown


install.packages("palmerpenguins")

#Problem 1

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
```
#load dataset
```{r, message = FALSE, warning = FALSE}
data("penguins", package = "palmerpenguins")
```
find names of the variables are `r names(penguins)`


find number of rows:
`r nrow(penguins)`

find number of columns:
`r ncol(penguins)`

find the mean of flipper length:
`r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`

#scatter plot of flipper_length_mm (y) vs bill_length_mm (x)
```{r, message = FALSE} 
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species))+ geom_point()

#save the scatter plot
ggsave("scatter_plot.pdf")

```

#Problem 2
```{r, message = FALSE, warning = FALSE}
#create a data frame
hw1_df = tibble(
  #create a normal sample of size of 10
  norm_samp = rnorm(10),
  #elements of the sample are greater than 0
  norm_samp_pos = norm_samp > 0,
  #create a character vector of length 10
  vec_char = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
  #create a factor vector of length 10, with 3 different factor “levels” 
  vec_factor = factor(c("A", "A", "A", "B", "B", "B", "C", "C", "C", "C"), levels = c("A", "B", "C")),
)
#try to find the mean of each variable
mean(pull(hw1_df, norm_samp))
mean(pull(hw1_df, norm_samp_pos))
mean(pull(hw1_df, vec_char))
mean(pull(hw1_df, vec_factor))

#The mean can be taken from logical vector but not character and factor vectors

#try as.numeric
as.numeric(pull(hw1_df, norm_samp_pos))
as.numeric(pull(hw1_df, vec_char))
as.numeric(pull(hw1_df, vec_factor))

```
As we apply the as.numeric function to the logical, character, and factor variables, logical factor can be numeric to be either 1 or 0 as corresponds to true and false, 
character variables cannot be convert to numeric, 
and factor can be convert to numeric as they only appear their levels 1 to 3
